Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-28 text/src/article.tex
Fix vim fold markder
Minor corrections

The form of the scaffold file is a list of entries. Each entry corresponds to
a length of sequence in the the draft genome sequence. When generating the
genome sequence from the scaffold file each entry is processed in order. Each
of the nucleotide sequence specified by the scaffold file entries are
concatenated together to produce the draft genome sequence. Each entry in the
scaffold file may have attributes which define whether a sub-sequence or the
reverse complement of the sequence should be used is the scaffold. The types of
attributes are outlined in the Results and Discussion section below.\pb

>>>>

The form of the scaffold file is a list of entries. Each entry corresponds to
a length of sequence in the the draft genome sequence. When generating the
genome sequence from the scaffold file each entry is processed in order. Each
of the nucleotide sequence specified by the scaffold file entries are
concatenated together to produce the draft genome sequence. Each entry in the
scaffold file may have attributes that define whether a sub-sequence or the
reverse complement of the sequence should be used. The types of attributes are
outlined in the Results and Discussion section below.\pb
